---
title: "CLT problem 1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
A large freight elevator can transport a maximum of 9800 pounds. Suppose a load of cargo containing 49 boxes must be
transported via the elevator. Experience has shown that the weight of boxes of this type of cargo follows a distribution with
mean µ = 205 pounds and standard deviation σ = 15 pounds. Based on this information, what is the probability that all 49
boxes can be safely loaded onto the freight elevator and transported ?

First, we need to list our given variables:
Max. weight = 9800 lbs
n = 49 boxes
mean = 205
sd = 15

Let Xn be the variable representing the weight of each of the boxes 
Xn  ∼  ( µ = 205, σ = 15) 
n=49/ maxload=9800
Since n>30 and according to the CLT: ∑Xn  ∼ N(nµ, σ√n), that is ∑Xn  ∼ N(10045,105)
The probability that all 49 boxes will be loaded is the probability that ∑Xn < 9800 
i.e
p(∑Xn<9800)=p(z<(9800-10045)/105)
           =p(z<-2.33)
           =0.0099

We can find a solution by using z-score. Using above notations:
z = (Max.weight - n * (mean))/(sqrt(n) * sd)
```{r}
z.sc <- (9800 - 49* (205))/(sqrt(49)* 15)
z.sc
```
That's our z-score. You can check the table for the probability, but (thanks, Yin) we can also plug z-score value into a normal distribution function:
```{r}
pnorm(z.sc)
```
This value is very close to the one in the table.
So, to answer the original question, the probability that 49 boxes can be loaded into the elevator safely is 0.098 percent.
