---
title: "study_session 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Textbook question 6.64 solution
Restaurant Sales The daily sales total (excepting Saturday) at a small restaurant has a probability
distribution that is approximately normal, with a mean m equal to $1230 per day and a standard deviation equal to $120.
a. What is the probability that the sales will exceed $1400 for a given day?

```{r}
pnorm(1400, mean = 1230, sd = 120, lower.tail = FALSE)

```
The probability is 0.08%. We used "lower.tail= FALSE" argument here, but you could just as well do 1 - pnorm instead.
```{r}
1 - pnorm(1400, mean = 1230, sd = 120)
```
b. The restaurant must have at least $1000 in sales per day to break even. What is the probability that
on a given day the restaurant will not break even?

```{r}
pnorm(1000, mean = 1230, sd = 120)
```
Probability of 0.03%. 

Textbook question 6.76 solution
A cross between two peony plants-one with red petals and one with streaky petals-produced offspring plants
with red petals 75% of the time. Suppose that 100 seeds from this cross were collected and germinated,
and x, the number of plants with red petals, was recorded.
a. What is the exact probability distribution for x?
```{r}
barplot(dbinom(0:100, size=100, prob=0.75))
```
This is a binomial distribution, since we have 2 outcomes, red petals and streaky petals.

b. Is it appropriate to approximate the distribution in
part a using the normal distribution? Explain.

Yes, we can see that above pretty clearly. Additionally, we can test whether a normal distribution may be used to approximate the binomial distribution.
If np >= 5 and nq >= 5,where q = 1 - p, normal distribution can be used. Here we have 49*0.75 = 36.75 and 49 * 0.25 = 12.25.

c. Use an appropriate method to find the approximate
probability that between 70 and 80 (inclusive) offspring
plants have red flowers.


```{r}
prob.1 <- pbinom(69, size = 100, prob = 0.75)
prob.2 <- pbinom(80, size = 100, prob = 0.75)
prob.2 - prob.1
```

We can also calculate that using a normal distribution. We need to find the mean and standard deviation:
mean = np
sqrt(m*q), where q = 1 - p

```{r}
m <- 100*0.75
s.t.d. <- sqrt(m * 0.25)
n.prob.1 <- pnorm(69, m, s.t.d.)
n.prob.2 <- pnorm(80, m, s.t.d.)
n.prob.2 - n.prob.1
```

We can see that while different, the probability we get from binomail distribution and from normal distribution are almost identical.


d. What is the probability that 53 or fewer offspring
plants had red flowers? Is this an unusual occurrence?
```{r}
prob.3 <- pbinom(53, size = 100, prob = 0.75)
prob.3
```
This is very unusual, if we are to believe this number.My guess is "no chance in Hell" is the answer here.

e. If you actually observed 53 of 100 offspring plants
with red flowers, and if you were certain that the
genetic ratio 3:1 was correct, what other explanation
could you give for this unusual occurrence?

During discussion we decided that is you are confident that both 53 out fo 100 and 0.75% probability are true, than there must be an uknown independent variable which affects our sample.






























